\section{Solution Approach}
\label{sec:sol}
With our problem definition narrowed down to three sub-questions, we build a social graph model to address these research questions. 
After we have the social graph, we select the appropriate network metrics to measure the aspects of innovation.
With these metrics, we can answer the research questions as well as provide empirical evidence to verify our rankings.

\subsection{Inventor Network Model}
\label{sec:model}
Our social graph models two aspects of the inventor network:  `Which inventors
and organizations have joint patents?' and `How many patents cite a certain
patent?'. These two networks abstracts out just enough information to address
our three sub-problems discussed in Section~\ref{sec:prob}. We describe our graph models in detail below:

\paragraph{Graph G1: Co-inventorship Graph}

	\begin{itemize}
	% \squish
		\item {Vertices:} Inventors  ($I_1$, $I_2$, ...)
		\item {Edges:} Signify co-inventorship on one / more patents
	\end{itemize}

There exists an edge between $I_1$ and $I_2$ if these two inventors have a
joint patent. Since two inventors can have multiple joint patents, the weight
signifies the number of joint patents

\paragraph{Graph G2: Citation Graph.}

	\begin{itemize}
	% \squish
		\item {Vertices:} Patents ($P_1$, $P_2$, ...)
		\item {Edges:} Citations 
	\end{itemize}

There exists a directed `citation' edge from $P_1$ to $P_2$ if $P_1$ cites $P_2$.

\subsection{Definitions \& Insights}

	\begin{itemize}
	% \squish
		\item {\em Collaborative distance.} For any two inventors, we define
		the collaborative distance as the length of the shortest path in
		Graph G1.
		\item {\em Invention impact.} For a given inventor / organization, we define his /
		her invention impact as the sum of degree centrality for
		all the patents from Graph G2 of this inventor / organization.
	\end{itemize}

% \subsection{Insight}

In our model, the impact of an inventor is measured by the total number of citations
to the patents that he / she invents. Thus, intuitively, the more is the sum of degree
centrality measure, the inventor is more `impactful'. Similarly, we use
collaborative distance to measure the `connectedness' between two inventors.
Thus, intuitively, the smaller the collaborative distance, the closer they are
to each other in terms of connection in the graph.  In a nutshell, the answers
to our questions framed in our problem description follow from these insights:

\paragraph{Answer 1.} Check the correlation between collaborative distance and invention impact.
If inventors with smaller value of collaborative distance from an impactful inventor have 
high value for invention impact, then we can say that collaborative distance from an impactful inventor
affects the invention impact of an individual inventor.

\paragraph{Answer 2.} Check the correlation between collaborative distance and organization.
Check whether most inventors within the same organization as the impactful inventor
have smaller collaborative distance or inventors outside the orgranization have
smaller distance.

\paragraph{Answer 3.} Check the correlation between invention impact and organization.
Calculate the sum of degree centralities from Graph G2 for each organization and rank the 
organization depending on the centrality measure. Organization with highest sum of degree
centralities is the most impactful and is ranked one. Compare this list with publicly available
list of innovative organization. Similarity in the two list indicates that total citations for the patents
is a correct metric to decide the invention impact of an organization.


